---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "README-"
)
```

`flowdockr` is an R package to work wih the [Flowdock API](https://www.flowdock.com/api)

_Heavily_ based on [`slackr`](https://github.com/hrbrmstr/slackr).

The following functions are implemented:

- `dev_flow`:	Send the graphics contents of the current device to a Flowdock flow
- `flow_file`:	Upload a file to a flow
- `flow_msg`:	Post a message to a flow
- `flow_r`:	Post R objects to Flowdock
- `get_flow_info`:	Retrieve flow metadata
- `ggflow`:	Send a rendered ggplot object to Flowdock
- `list_flows`:	List flows
- `save_flow`:	Save R objects to an RData file on Flowdock

### News

- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/flowdockr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(flowdockr)

# current verison
packageVersion("flowdockr")

```

### Test Results

```{r}
library(flowdockr)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.